---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gdallocationinfo

<!-- badges: start -->
<!-- badges: end -->

The goal of gdallocationinfo is to look up values on a raster source. 

Input is a character string to the GDAL readable source, and matrix of lon,lat. 

## Installation

You can install the development version of gdallocationinfo like so:

``` r
devtools::install_github("hypertidy/gdallocationinfo")
```

## Example

This is a basic example, lookup GEBCO 2023 values on world cities:

```{r example}
library(gdallocationinfo)
#options(parallelly.fork.enable = TRUE, future.rng.onMisuse = "ignore")
#library(furrr); plan(multicore)

loc <- locationinfo("/vsicurl/https://gebco2023.s3.valeria.science/gebco_2023_land_cog.tif", 
                    as.matrix(maps::world.cities[1:1000, c("long", "lat")]))

str(loc)
#plan(sequential)
maps::world.cities$name[which.max(loc)]
maps::world.cities$name[which.min(loc)]
```


## Code of Conduct
  
Please note that the gdallocationinfo project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
